The \project{unRAVE} catalog

### 2016-09-08 article/unrave.tex
Update text and figures to v0.96

In Figure \ref{fig:joint-model-differences} we show the differences in effective 
temperature $\teff$ and surface gravity $\logg$ between: the main-sequence model 
(Section~\ref{sec:unevolved-star-model}) and the simplest model (Section~
\ref{sec:a-simple-model}); and the differences between the red giant branch model 
(Section~\ref{sec:evolved-star-model}) and the simplest model (Section 
\ref{sec:a-simple-model}).  We have scaled the differences in $\teff$ and $\logg$ 
to make the central peak near $(0, 0)$ to be approximately isotropic by setting
	$\delta_{T_{\rm eff}} = 90$~K for the main-sequence model, 
	$\delta_{T_{\rm eff}} = 50$~K for the giant model, and 
	$\delta_{\log{g}} = 0.15$~dex for both models.
It is important to note that these $\delta$ values do not represent any kind of 
intrinsic uncertainty or precision: they are merely normalization factors.  Adopting
substantially different scaling factors would produce in clear inconsistencies in our
results (e.g., sub-giants being misclassified as giants).  Therefore we chose these 
factors empirically to make the distributions in Figure \ref{fig:joint-model-differences}
approximately isotropic, and to some extent, comparable.  In Figure 
\ref{fig:joint-model-differences} the stars within the peak at $(0, 0)$ represent 
objects where the simple model and the comparison model both report similar labels.  
The artefacts seen in the Hertzsprung-Russell diagrams in Figure \ref{fig:test-set-density} 
are also present in Figure \ref{fig:joint-model-differences} as over-densities far away
from the central peak.  Therefore, we can adopt the scaled distance in labels 
$\teff$ and $\logg$ from the joint model to the main-sequence model $d_{ms}$,
\begin{eqnarray}
	d_{ms} & = & \left(\frac{T_{{\rm eff},ms} - T_{{\rm eff},joint}}{\delta_{T_{{\rm eff},ms}}}\right)^2 + \left(\frac{\log{g}_{ms} - \log{g}_{joint}}{\delta_{\log{g},ms}}\right)^2 \quad .
\end{eqnarray}

\stub{Warning: The metallicity correction may disappear -- I am trying to fix that}
However when adopting a similar distance metric for the giant model, we found that the
giant model and the joint model produced similar label estimates (with low $\chi_r^2$
values) for metal-poor ($[{\rm Fe/H]} < -1$) dwarf stars near the turn-off.  The similarity
in estimated labels occurred in $\teff$, $\logg$, \emph{and} [Fe/H], implying that we
could not use the difference between $[{\rm Fe/H}]_{giant} - [{\rm Fe/H]}]_{joint}$
as a term that would benefit the main-sequence model.  As a result, our joint estimate 
for metal-poor dwarf stars that overlap with high-resolution studies
\citep{Reddy_2003,Reddy_2006,Bensby_2014,Valenti_Fischer_2005},
would appear as metal-poor giant stars, because the giant star model would have a much
smaller distance metric than the main-sequence model.  It is reasonable to assert that
this issue may be complicated by the increased complexity, or flexibility, of the giant
star model relative to the main-sequence model.  In any case, we found that by empirically
penalizing the giant model distance metric by absolute metallicity,
\begin{eqnarray}
	d_{giant} & = & \left(\frac{T_{{\rm eff},giant} - T_{{\rm eff},joint}}{\delta_{T_{{\rm eff},giant}}}\right)^2 + \left(\frac{\log{g}_{giant} - \log{g}_{joint}}{\delta_{\log{g},giant}}\right)^2  + \lvert[{\rm Fe/H}]_{joint}\rvert  \quad ,
\end{eqnarray}

\noindent{}the weighting of dwarfs was no longer a function of joint metallicity, and this
issue was resolved without introducing new artefacts. Using these distance metrics we 
then derived the weights,
\begin{eqnarray}
	w_{ms} = \frac{1}{{d_{ms}}^2} & \text{and} & w_{giant} = \frac{1}{{d_{giant}}^2} \quad ,
\end{eqnarray}

@@

The weighted $\teff$ and $\logg$ values for stars meeting different
S/N constraints are shown in Figure \ref{fig:test-set-hrd}, both in logarithmic density
and mean metallicity.  The artefacts from individual models are no longer 
apparent, and the rich structure of the Hertzsprung-Russell is visible.  Despite
this, there are a number of caveats introduced by the choices we have made to
combine estimates from multiple models. We discuss these issues in detail in
Section \ref{sec:discussion}.

@@

The \rave\ survey performed repeat observations for 43,918 stars with time 
intervals ranging from a few hours to up to four years.  This timing was 
constructed to be quasi-logarithmic such that spectroscopic binaries could
be optimally identified. Most of the stars that were observed multiple times
were only observed twice, with thirteen visits being the maximum number 
of observations for any target.  These repeat observations allow us to 
quantify the level of (in)correctness in our formal errors.  For every star
with multiple visits we constructed a high S/N stacked spectrum for that
star, weighted by the inverse variances in the individual visit spectra.

>>>>

In Figure \ref{fig:joint-model-differences} we show the differences in effective 
temperature $\teff$ and surface gravity $\logg$ between: the main-sequence model 
(Section~\ref{sec:unevolved-star-model}) and the simplest model (Section~
\ref{sec:a-simple-model}); and the differences between the red giant branch model 
(Section~\ref{sec:evolved-star-model}) and the simplest model (Section 
\ref{sec:a-simple-model}).  We have scaled the differences in $\teff$ and $\logg$ 
to make the central peak near $(0, 0)$ to be approximately isotropic by setting
	$\delta_{T_{\rm eff}} = 90$~K for the main-sequence model, 
	$\delta_{T_{\rm eff}} = 50$~K for the giant model, and 
	$\delta_{\log{g}} = 0.15$~dex for both models.
It is important to note that these $\delta$ values do not represent any kind of 
intrinsic uncertainty or precision: they are merely normalization factors.  Adopting
substantially different scaling factors would produce in clear inconsistencies in our
results (e.g., sub-giants being misclassified as giants).  Therefore we chose these 
factors empirically to make the distributions in Figure \ref{fig:joint-model-differences}
approximately isotropic, and to some extent, comparable.  In Figure 
\ref{fig:joint-model-differences} the stars within the peak at $(0, 0)$ represent 
objects where the simple model and the comparison model both report similar labels.  
The artefacts seen in the Hertzsprung-Russell diagrams in Figure \ref{fig:test-set-density} 
are also present in Figure \ref{fig:joint-model-differences} as over-densities far away
from the central peak.  Therefore, we can adopt the scaled distance in labels 
$\teff$ and $\logg$ from the simplest model to the main-sequence model $d_{ms}$,
\begin{eqnarray}
	d_{ms} & = & \left(\frac{T_{{\rm eff},ms} - T_{{\rm eff},joint}}{\delta_{T_{{\rm eff},ms}}}\right)^2 + \left(\frac{\log{g}_{ms} - \log{g}_{joint}}{\delta_{\log{g},ms}}\right)^2 \quad ,
\end{eqnarray}

\noindent{}and the scaled distance from the simplest model to the giant model $d_{giant}$,
\begin{eqnarray}
	d_{giant} & = & \left(\frac{T_{{\rm eff},giant} - T_{{\rm eff},joint}}{\delta_{T_{{\rm eff},giant}}}\right)^2 + \left(\frac{\log{g}_{giant} - \log{g}_{joint}}{\delta_{\log{g},giant}}\right)^2  \quad ,
\label{eq:d_giant}
\end{eqnarray}

\noindent{}to derive the weights,
\begin{eqnarray}
	w_{ms} = \frac{1}{{d_{ms}}^2} & \text{and} & w_{giant} = \frac{1}{{d_{giant}}^2} \quad ,
\end{eqnarray}

@@

The weighted $\teff$ and $\logg$ values for stars meeting different
S/N constraints are shown in Figure \ref{fig:test-set-hrd}, both in logarithmic density
and mean metallicity.  The artefacts from individual models are no longer 
apparent, and stars across the full Hertzsprung-Russell diagram are visible.
However, there are a number of caveats introduced by the choices we have made to
combine estimates from multiple models.  We discuss these issues in detail in
Section \ref{sec:discussion}.

@@

The \rave\ survey performed repeat observations for 43,918 stars with time 
intervals ranging from a few hours to up to four years.  This timing was 
constructed to be quasi-logarithmic such that spectroscopic binaries could
be optimally identified. Most of the stars that were observed multiple times
were only observed twice, with thirteen visits being the maximum number 
of observations for any target.  These repeat observations allow us to 
quantify the level of (in)correctness in our formal errors.

For every star
with multiple visits we constructed a high S/N stacked spectrum for that
star, weighted by the inverse variances in the individual visit spectra.
